### 2012-10-02 docs/runtime_parameters/runtime_parameters.tex
add a chapter label.  Update the parameter list
update parameters, remove redundancy in intro

\section{Runtime Parameters}

The following tables list the runtime parameters available to
all MAESTRO problems.  Problem-specific runtime parameters are not
shown here.

@@

\rowcolor{tableShade}
\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\
\rowcolor{tableShade}
\verb=  use_eos_coulomb  = &   use the Coulomb corrections between ions (if supported by the EOS)  &  .true. \\
\verb=  use_eos_e_instead_of_h  = &   In deriving the temperature from the $h$, first subtract off $p_0/\rho$ to define $e$, and use that as the input to the EOS.  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  sdc_iters  = &   how many SDC iteractions to take (requires the code be compiled with {\tt SDC := t}  &  4 \\

@@

@@

\verb=  spherical_in  = &   set to 1 if you are doing a spherical problem  &  0 \\

@@

\verb=  enthalpy_pred_type  = &   predict\_rhohprime = 1; \newline predict\_h = 2; \newline predict\_T\_then\_rhohprime = 3; \newline predict\_T\_then\_h = 4; \newline predict\_hprime = 5; \newline predict\_Tprime\_then\_h = 6.  &  predict\_rhohprime \\

@@

@@

@@

\verb=  use_linear_grav_in_beta  = &   how to represent gravity in the beta0 integration: .true. = piecewise linear .false. = piecewise constant  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\rowcolor{tableShade}
\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\rowcolor{tableShade}
\verb=  use_hypre  = &   use the hypre library  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  check_base_name  = &   prefix to use in checkpoint file names  &  "chk" \\
\verb=  chk_int  = &   Number of timesteps between writing a checkpoint file  &  0 \\
\rowcolor{tableShade}
\verb=  diag_buf_size  = &   number of timesteps to buffer diagnostic output information before writing (note: not implemented for all problems)  &  10 \\
\verb=  lUsingNFiles  = &   If .true., use nOutFiles processors to write checkpoint and plotfiles. Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  .true. \\
\rowcolor{tableShade}
\verb=  nOutFiles  = &   If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  64 \\
\verb=  plot_Hext  = &   plot external heating (Hext) in plotfile  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_Hnuc  = &   plot nuclear energy generation rate (Hnuc) in plotfile  &  .true. \\
\verb=  plot_ad_excess  = &   plot the adiabatic excess  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_base  = &   plot w0\_x, w0\_y, w0\_z, divw0, rho0, rhoh0, h0, and p0 in plotfile  &  .false. \\
\verb=  plot_base_name  = &   prefix to use in plotfile file names  &  "plt" \\
\rowcolor{tableShade}
\verb=  plot_cs  = &   plot soundspeed  &  .false. \\
\verb=  plot_deltat  = &   rather than use a plot interval, plot a file after the solution has advanced past plot\_deltat in time  &  -1.d0 \\
\rowcolor{tableShade}
\verb=  plot_eta  = &   plot $\etarho$ in plotfile  &  .false. \\
\verb=  plot_gpi  = &   plot pi and grad(pi)  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_h_with_use_tfromp  = &   Turn on storing of enthalpy-based quantities in the plotfile when we are running with {\tt use\_tfromp}  &  .true. \\
\verb=  plot_int  = &   plot interval  &  0 \\
\rowcolor{tableShade}
\verb=  plot_omegadot  = &   plot omegadot in plotfile  &  .true. \\
\verb=  plot_processors  = &   create a field in the plotfile storing the processor number for each zone  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_spec  = &   plot species and omegadot in plotfile  &  .true. \\
\verb=  plot_trac  = &   plot tracers in plotfile  &  .false. \\
\rowcolor{tableShade}
\verb=  single_prec_plotfiles  = &   store the state data in single precision  &  .false. \\

>>>>

\label{ch:parameters}

@@

\rowcolor{tableShade}
\verb=  small_dens  = &    &  1.d-5 \\
\verb=  small_temp  = &    &  5.d6 \\
\rowcolor{tableShade}
\verb=  use_eos_e_instead_of_h  = &   In deriving the temperature from the $h$, first subtract off $p_0/\rho$ to define $e$, and use that as the input to the EOS.  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  sdc_couple_mac_velocity  = &   recompute MAC velocity at the beginning of each SDC iter if .false., only recompute MAC velocity at the beginning of the first iter  &  .false. \\
\verb=  sdc_hold_mac_velocity  = &   if true, never recompute MAC velocity, no matter what the other sdc flags are  &  .false. \\
\rowcolor{tableShade}
\verb=  sdc_iters  = &   how many SDC iteractions to take (requires the code be compiled with {\tt SDC := t}  &  1 \\

@@

\verb=  do_2d_planar_octant  = &   Set to 1 if using the 2D simplified (planar) model of an octant.  &  0 \\

@@

\verb=  spherical_in  = &   Set to 1 if you are doing a spherical problem.  &  0 \\

@@

\verb=  enthalpy_pred_type  = &   predict\_rhoh = 0; \newline predict\_rhohprime = 1; \newline predict\_h = 2; \newline predict\_T\_then\_rhohprime = 3; \newline predict\_T\_then\_h = 4; \newline predict\_hprime = 5; \newline predict\_Tprime\_then\_h = 6.  &  predict\_rhohprime \\

@@

\verb=  use_alt_energy_fix  = &   modify the momentum equation to have $(\beta_0/\rho) \nabla (\pi/\beta_0)$ instead of just $(1/\rho) \nabla (\pi)$  &  .false. \\

@@

\verb=  use_linear_grav_in_beta  = &   how to represent gravity in the $\beta_0$ integration: .true. = piecewise linear .false. = piecewise constant  &  .false. \\

@@

@@

\rowcolor{tableShade}
\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\
\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\
\verb=  max_mg_bottom_nlevels  = &   if mg\_bottom\_solver == 4, then how many mg levels can the bottom solver mgt object have  &  1000 \\
\rowcolor{tableShade}
\verb=  mg_bottom_nu  = &   number of smoothing iterations to do after the multigrid bottom solver  &  10 \\
\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\rowcolor{tableShade}
\verb=  mg_verbose  = &   Verbsoity of the multigrid solver, but not the bottom solver.  &  0 \\
\verb=  use_hypre  = &   use the hypre library  &  .false. \\

@@

\rowcolor{tableShade}
\verb=  check_base_name  = &   prefix to use in checkpoint file names  &  "chk" \\
\verb=  chk_int  = &   Number of timesteps between writing a checkpoint file  &  0 \\
\rowcolor{tableShade}
\verb=  diag_buf_size  = &   number of timesteps to buffer diagnostic output information before writing (note: not implemented for all problems)  &  10 \\
\verb=  lUsingNFiles  = &   If .true., use nOutFiles processors to write checkpoint and plotfiles. Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  .true. \\
\rowcolor{tableShade}
\verb=  nOutFiles  = &   If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  64 \\
\verb=  plot_Hext  = &   plot external heating (Hext) in plotfile  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_Hnuc  = &   plot nuclear energy generation rate (Hnuc) in plotfile  &  .true. \\
\verb=  plot_ad_excess  = &   plot the adiabatic excess  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_base  = &   plot w0\_x, w0\_y, w0\_z, divw0, rho0, rhoh0, h0, and p0 in plotfile  &  .false. \\
\verb=  plot_base_name  = &   prefix to use in plotfile file names  &  "plt" \\
\rowcolor{tableShade}
\verb=  plot_cs  = &   plot soundspeed  &  .false. \\
\verb=  plot_deltat  = &   rather than use a plot interval, plot a file after the solution has advanced past plot\_deltat in time  &  -1.d0 \\
\rowcolor{tableShade}
\verb=  plot_eta  = &   plot $\etarho$ in plotfile  &  .false. \\
\verb=  plot_gpi  = &   plot pi and grad(pi)  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_h_with_use_tfromp  = &   Turn on storing of enthalpy-based quantities in the plotfile when we are running with {\tt use\_tfromp}  &  .true. \\
\verb=  plot_int  = &   plot interval  &  0 \\
\rowcolor{tableShade}
\verb=  plot_omegadot  = &   plot omegadot in plotfile  &  .true. \\
\verb=  plot_pidivu  = &   plot pi * div(U) -- this is a measure of conservation of energy  &  .false. \\
\rowcolor{tableShade}
\verb=  plot_processors  = &   create a field in the plotfile storing the processor number for each zone  &  .false. \\
\verb=  plot_spec  = &   plot species and omegadot in plotfile  &  .true. \\
\rowcolor{tableShade}
\verb=  plot_trac  = &   plot tracers in plotfile  &  .false. \\
\verb=  single_prec_plotfiles  = &   store the state data in single precision  &  .false. \\
